A SIMPLE AND EFFICIENT ALGORITHM FOR COMPUTING APPROXIMATE NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION

### 2015-09-26 paper.tex
ran aspell on .tex

\maketitle
\begin{abstract}
We present a simple primal-dual algorithm for
  computing approximate Nash-equilibria in two-person zero-sum
  sequential games with  incomplete information and perfect recall
  (like Texas Hold'em poker). Our algorithm only performs basic
  iterations (i.e matvec multiplications, clipping, etc., and no calls
  to external first-order oracles, no matrix inversions, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with incomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  which allows us to encode any such game
  as a matrix game with convex polytopial profiles. We prove that
  the number of iterations needed to produce a Nash-equilibrium with a
  given precision is inversely proportional to the
  precision. By way of demonstration, we also present experimental
  results on simulated and real games (Kuhn poker).
\end{abstract}

>>>>

\maketitle
\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash equilibria in two-person zero-sum sequential games with
incomplete information and perfect recall (like Texas Hold'em
poker). Our algorithm only performs basic iterations (i.e matvec
multiplications, clipping, etc., and no calls to external first-order
oracles, no matrix inversions, etc.) and is applicable to a broad
class of two-person zero-sum games including simultaneous games and
sequential games with incomplete information and perfect recall. The
applicability to the latter kind of games is thanks to the
sequence-form representation which allows us to encode any such game
as a matrix game with convex polytopial profiles. We prove that the
number of iterations needed to produce a Nash equilibrium with a given
precision is inversely proportional to the precision. As
proof-of-concept, we also present experimental results on simulated
and real games (Kuhn poker).
\end{abstract}
